Magnetised Polish doughnuts revisited

### 2017-07-10 paper_revised_v2/paper_revised_v2.tex
some small rewording

To reduce the number of free parameters to build the initial models we do as in~\citet{Komissarov:2006} and fix the values of the equation of state exponents, $\kappa$ and $\lambda$, and of the {\bf enthalpy density} at the disc centre, $w_{\mathrm{c}}$. More precisely, we choose $\kappa = \lambda = 4/3$ and $w_{\mathrm{c}} = 1$. This still leaves us with five parameters to control the size, shape, thickness, and magnetisation of the disc, namely the magnetisation parameter $\beta_{\mathrm{m}_{\mathrm{c}}}$, the parameters of the angular momentum distribution $\beta$ and $\gamma$, the black hole spin parameter $a$, and the inner radius of the disc $r_{\mathrm{in}}$. We build a series of 45 models, whose main features are summarised in Table~\ref{table:1} (for $\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}$, i.e.~models where the effects of the magnetisation are unimportant), Table~\ref{table:2} ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$, i.e.~equipartition models), and Table~\ref{table:3} ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}$, i.e.~highly-magnetised models). {\bf We have built models with very small values of $\beta_{\mathrm{m}_{\mathrm{c}}}$, such as  $\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-20}$ (extremely high magnetisation) without encountering numerical difficulties. In practice we have found that there are no qualitative differences in the structure of the discs once $\beta_{\mathrm{m}_{\mathrm{c}}}$ becomes smaller than a sufficiently small value, about $\beta_{\mathrm{m}_{\mathrm{c}}}=10^{-3}$. This is the reason why we choose that particular value as our lower limit in the figures and tables of the manuscript.}

>>>>

To reduce the number of free parameters to build the initial models we do as in~\citet{Komissarov:2006} and fix the values of the equation of state exponents, $\kappa$ and $\lambda$, and of the {\bf enthalpy density} at the disc centre, $w_{\mathrm{c}}$. More precisely, we choose $\kappa = \lambda = 4/3$ and $w_{\mathrm{c}} = 1$. This still leaves us with five parameters to control the size, shape, thickness, and magnetisation of the disc, namely the magnetisation parameter $\beta_{\mathrm{m}_{\mathrm{c}}}$, the parameters of the angular momentum distribution $\beta$ and $\gamma$, the black hole spin parameter $a$, and the inner radius of the disc $r_{\mathrm{in}}$. We build a series of 45 models, whose main features are summarised in Table~\ref{table:1} (for $\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{3}$, i.e.~models where the effects of the magnetisation are unimportant), Table~\ref{table:2} ($\beta_{\mathrm{m}_{\mathrm{c}}} = 1$, i.e.~equipartition models), and Table~\ref{table:3} ($\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-3}$, i.e.~highly-magnetised models). {\bf We note that we can build models with very small values of $\beta_{\mathrm{m}_{\mathrm{c}}}$, such as  e.g.~$\beta_{\mathrm{m}_{\mathrm{c}}} = 10^{-20}$ (extremely high magnetisation) without encountering numerical difficulties. No qualitative differences in the structure of the discs are found once $\beta_{\mathrm{m}_{\mathrm{c}}}$ becomes smaller than a sufficiently small value, about $\beta_{\mathrm{m}_{\mathrm{c}}}=10^{-3}$. This is the reason why we choose that particular value as our lower limit in the figures and tables of the manuscript.}
